---
title: "Arrhythmia"
output: html_document
---
```{r}
rm(list=ls())
```
This is an analysis on changes in P/R ratio and Heart rate variability (HRV) in response to arrhythmia and myocradial infarction dataset.

## Loading libs and data
We first load some necessary libs
```{r}
library(ggplot2)
library(data.table)
library(readxl)
source('multiplot.R')
```

And then load arrhythmia
```{r}
dataset <- read_excel("E:/MY_THESIS/data analysis/arrhythmia.xlsx")
dataset = as.data.table(dataset)

print(dataset)
```

## Main analysis
### Mean and std PR ratio analysis
We take the summary fo the dataset about the mean of PR ratio
```{r}
data_stats <- summarySE(dataset, measurevar = "MeanPR")
data_stats
```

Plot 95% confident interval
```{r}
ggplot(data_stats, aes(x = 0, y = MeanPR)) + 
  geom_errorbar(aes(ymin=MeanPR-ci, ymax=MeanPR+ci), width=.1) + 
  geom_point()
```

And summary of the dataset about the std PR ratio 
```{r}
data_stats <- summarySE(dataset, measurevar = "StdPR")
data_stats
```

Plot 95% confident interval
```{r}
ggplot(data_stats, aes(x = 0, y = StdPR)) + 
  geom_errorbar(aes(ymin=StdPR-ci, ymax=StdPR+ci), width=.1) + 
  geom_point()
```

Boxplot
```{r}
compare_min = ggplot(dataset, aes(x=0, y=MeanPR)) + geom_boxplot() + geom_point() + ylim(0, 0.75) + ggtitle("Mean PR ratio")
compare_max = ggplot(dataset, aes(x=0, y=StdPR)) + geom_boxplot() + geom_point() + ylim(0, 0.25) + ggtitle("std PR ratio")

multiplot(compare_min, compare_max, cols = 2)
```

***Conclusion: the threshold of PR ratio should be from 0.3 to 0.375 and the threshold of std of PR ratio is from 0.1 to 0.12***

### Mean and std of HRV:
We take the summary fo the dataset about the mean of PR ratio
```{r}
data_stats <- summarySE(dataset, measurevar = "MeanHRV")
data_stats
```

Plot 95% confident interval
```{r}
ggplot(data_stats, aes(x = 0, y = MeanHRV)) + 
  geom_errorbar(aes(ymin=MeanHRV-ci, ymax=MeanHRV+ci), width=.1) + 
  geom_point()
```

And summary of the dataset about the std PR ratio 
```{r}
data_stats <- summarySE(dataset, measurevar = "StdHRV")
data_stats
```

Plot 95% confident interval
```{r}
ggplot(data_stats, aes(x = 0, y = StdHRV)) + 
  geom_errorbar(aes(ymin=StdHRV-ci, ymax=StdHRV+ci), width=.1) + 
  geom_point()
```

Boxplot
```{r}
compare_min = ggplot(dataset, aes(x=0, y=MeanHRV)) + geom_boxplot() + geom_point() + ylim(0, 200) +ggtitle("Mean HRV")
compare_max = ggplot(dataset, aes(x=0, y=StdHRV)) + geom_boxplot() + geom_point() + ylim(0, 200) +ggtitle("std PR HRV")

multiplot(compare_min, compare_max, cols = 2)
```

***Conclusion: the threshold of HRV should be from 100 to 110, sine the std of HRV is so large, we ignore this figure***